Centralizers of higher enveloping algebras of Lie algebras

### 2020-08-31 draft.tex
small things

\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}

@@

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
:= {\frak Z}_{E_n}(\id_A)$.
\end{dfn}
When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$. Thus, the center of $A$ agrees with the traditional notion. See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.

@@

We now turn to proving Theorem~\ref{thm: centralizer}.

>>>>

\owen{I want to work with a colored operad $\Disk_n$ of round disks (or rectilinear boxes) in $\RR^n$.}

@@

\owen{Plus a version for $\Disk_n$ algebras}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
:= {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

When $n=1$ and $\cC$ is the category of vector spaces, 
the centralizer of $f: A \to B$ consists of elements in $B$ that commute with the image $f(A)$ inside~$B$. 
In particular, taking $f$ as the identity map, 
the center of $A$ defined above agrees with the traditional notion. 
See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.

@@

%We now turn to proving Theorem~\ref{thm: centralizer}.
